A framework for adaptive width control of dense contour-parallel toolpaths in {fused deposition modeling}\censornotice

### 2020-01-25 6_validation.tex
remove \revise macro everywhere

\revise{}
{
\subsection{Computational results}\label{sec_computational_results}
} % tew
We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
The data set is described in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices for analysis.
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library,
and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using \revise{$N=3$}{$N=2$}, all with a preferred bead width\revise{s}{} of \revise{$w^* = \SI{0.4}{\milli\meter}$}{$w^* = \SI{0.5}{\milli\meter}$ and using the widening meta-scheme to enforce a minimum printed feature size of $w_\text{min}=2r_\text{min}=\SI{0.3}{\milli\meter}$}.
The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.
\revise{}{We report on the total statistics summed over the whole data set, because averaging would be biased.}

\subsubsection{Accuracy}
We first evaluate the accuracy of different beading schemes in terms of the relative amount of the overfill and underfill. 
We construct the over- and underfill area by comparing the shapes covered by each extrusion move \revise{(\cref{segment_visualization_simple})}{} with each other and with the total shape of the boundary polygons. (For implementation details see Appendix~\ref{accuracy_calculation}.)
This results in polygonal shapes such as visualized in the top half of \cref{visualized_accuracy}:
there are orange shapes where the beads overlap and azure shapes in the voids in between the beads.
%
%
We compare the total area in \si{\milli\meter\squared} of these overfill and underfill shapes to the total area of the boundary for each sample in the data set
and report the average percentages in \revise{see }{}\cref{over_underfill}.
The inward distributed scheme has a calculated overfill of \revise{\SI{0.24}{\percent}}{\SI{0.30}{\percent}} and an underfill of \revise{\SI{0.17}{\percent}}{\SI{0.24}{\percent}}.
This is lower compared to the uniform scheme, which results in \revise{\SI{1.2}{\percent}}{\SI{1.63}{\percent}} overfill and \revise{\SI{1.7}{\percent}}{\SI{1.62}{\percent}} underfill in the data set.
\iffalse
names ['naive', 'Constant', 'Center', 'Distributed', 'InwardDistributed']
overfill [  1.63223926  22.21073295   0.37059604   0.45119725   0.30226112]
outer_underfill [ 0.04664107  0.03232884  0.04357603  0.03494708  0.03475748]
underfill [ 1.62009421  0.0712721   0.76886316  0.2440984   0.24461937]
\fi

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-widths.png}
\caption{Uniform}\label{TEST_naive_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-accuracy.png}
%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-widths.png}
%\caption{Single}\label{TEST_SingleBead_accuracy}
%\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-widths.png}
\caption{Centered}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-widths.png}
\caption{Inward \revise{}{($N=2$)}}\label{TEST_InwardDistributed_accuracy}
\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4.7cm}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-widths-legend.pdf}
\end{subfigure}
\caption{
Visualization of the overfills and underfills (top) and the widths (bottom) for various beading schemes.
Extrusion beads in gray tones,
overfill in orange,
underfill in azure,
narrow beads in blue
and wide beads in red.
\revise{New shape contains pointy wedge to see impact on minimal feature size}{In order to distinguish clearly from the Distributed scheme the Inward is limited to $N=2$.}
}
\label{visualized_accuracy}
\end{figure*}

\begin{figure*}
\centering
\setlength{\figheight}{0.25\textwidth}
\setlength{\figwidth}{0.32\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-over-underfill.pdf}
%\includegraphics[width=\figwidth]{sources-validation-overunderfill.pdf}
\caption{\revise{}{Over- and underfill}}
\label{over_underfill}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-print-time.pdf}
%\includegraphics[width=\figwidth]{sources-validation-smoothness.pdf}
\caption{\revise{}{Print time}}
\label{printtime}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-path-counts.pdf}
%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
\caption{\revise{}{Path counts}}
\label{pathcounts}
\end{subfigure}

\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-widths.pdf}
%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
\caption{\revise{}{Extrusion widths}}
\label{widthHistogram}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-angles.pdf}
%\includegraphics[width=\figwidth]{sources-validation-smoothnessNoTransition.pdf}
\caption{\revise{}{Site angles}}
\label{smoothness}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-computime2.pdf}
%\includegraphics[width=\figwidth]{sources-validation-computime2.pdf}
\caption{Computation time}
\label{computime}
\end{subfigure}

\caption{
Statistical analysis of the toolpaths from applying the uniform width technique and various beading schemes using our framework to a data set of 300 slices.
Note the use of a logarithmic scale \revise{}{in the bottom graphs }on the Y-axes and \revise{on some of}{for \subref{computime} on} the X-axes as well.
}
\label{statisticsfig}
\end{figure*}

\subsubsection{Uniformity}
We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.
\revise{
We calculated the mean and standard deviation of the bead width, sampled at \SI{1}{\micro\meter} along the toolpaths.
\cref{widthHistogram} shows the distribution of extrusion width for each scheme binned at intervals of \SI{10}{\micro\meter}.
}{
We binned the toolpaths into width bins at \SI{0.01}{\milli\meter} increments and determine the total toolpath length pertaining to each bin.
From these statistics we calculate the mean and standard deviation and report them in \cref{widthHistogram}.
}
We found that the mean width of the inward and evenly distributed schemes is close to preferred bead width of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme. 
These results show that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.
\revise{
We compared the width uniformity of the 6 outer beads for the inward and evenly distributed schemes, the distribution of these extrusion widths is shown in \cref{widthIndexedHistogram}. 
The outer beads of the inward distributed scheme deviate less from the preferred width compared to the evenly distributed scheme.
}{}

\revise{
\subsubsection{Smoothness of toolpaths}
In order to maintain a high printing speed, it is desirable that toolpaths have fewer and less sharp corners. 
We therefore measured the angle between consecutive extrusion segments generated by each scheme
and report on the occurrence of each angle in \cref{smoothness}.
All schemes show a higher number of corners for smaller angles with a peak towards \SI{180}{\degree} (straight).
We observe that compared to the uniform method our framework produces less acute angles which, but more obtuse angles.
The inward distributed scheme produces an order of magnitude less corners around \SI{150}{\degree}, compared to evenly distributed. 
We also investigated the effect of the transition regions on the smoothness of the toolpaths. 
\cref{smoothnessNoTransition} shows that introducing the transitions greatly reduces the number of corners around \SI{90}{\degree}. 
}{
\subsubsection{Print time}
The total time it takes to print a part is influenced not only by our back pressure compensation scheme, but also by the geometry of the toolpaths.
In order to separate these effects we report on the total print time when using back pressure compensation and when using a constant (maximum) movement speed in \cref{printtime}.
We estimate print times using a simulation of the Marlin firmware using the default movement settings of the setup described in \cref{print_results_section}.
While the idealized print time is predominantly determined by the total toolpath length, the print time using back pressure compensation is predominantly determined by the occurrence of wide beads, because they have a reduced the flow in \si{\milli\meter\cubed\per\second}.
Because of acceleration constraints imposed by the hardware the maximum movement speed is not reached near sharp corners.
We therefore also report on the angles of the bends in the toolpaths in \cref{smoothness}.
Furthermore, the print time is negatively affected by discontinuities in the extrusion process.
Between extrusions the printer needs to stop extrusion, travel to the next extrusion path and restart the extrusion process, which all take time.
For closed polygonal toolpaths we can start anywhere within the path, so we can optimize the starting location so as to minimize the travel time.
We therefore report both on the open and closed path count in \cref{pathcounts}.
}

@@

\revise{
Test prints were performed on a custom FDM hardware setup, with a standard \SI{0.4}{\milli\meter} nozzle and a filament extrusion drive directly mounted on the print head.
The firmware of the printer employs \emph{linear advance} for accurately realizing adaptive deposition width:
gaining the extra pressure required to change to a wider bead is realized by 'advancing' an extra amount of filament into the physical system~\cite{tronvoll2019investigating}.
We set the preferred width to $w^* = \SI{0.6}{\milli\meter}$, to avoid fluttered printing of lines narrower than the nozzle size.
We used a layer thickness of \SI{0.2}{\milli\meter} and a movement speed of \SI{10}{\milli\meter\per\second}.

The prints are shown in \cref{prints}.
Because of inaccuracies in the deposition control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
The prints which employ the uniform offsets technique show a lot of underfill, which impacts the visual quality of the print.
Moreover, in the case of the regular honeycomb there are several fully disconnected hexagons, which means the object falls apart.
The difference between the centered and the inward distributed schemes is less pronounced.
We can still see some loosely connected extrusion segments in both, which is attributable to inaccuracies in the extrusion system.
However, the middle of \cref{wedge_print} exhibits more defects in the regions where the centered scheme produces extreme bead widths.
The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.

\begin{figure}
\centering
\begin{subfigure}{\columnwidth}\centering
\setlength{\figwidth}{\columnwidth}
\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-naive-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-center-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-wedge-inward-edited.png}
\caption{Uniform (top), centered (mid) and inward distributed (bottom)}\label{wedge_print}
\end{subfigure}
\setlength{\figheight}{.38\columnwidth}
\setlength{\figheightTwo}{.47\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-naive.png}
\includegraphics[height=\figheight]{sources-applications-P3-print-hex-naive-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-naive-edited.png}
\caption{Uniform}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-center.png}
\includegraphics[height=\figheight]{sources-applications-P3-print-hex-center-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-center-edited.png}
\caption{Centered}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheightTwo]{sources-applications-gMAT-inward.png}
\includegraphics[height=\figheight]{sources-applications-P3-print-hex-inward-edited.png}
\includegraphics[width=\figwidth]{sources-applications-P3-print-UM-inward-edited.png}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the uniform scheme, centered scheme and the inward distributed scheme.
The uniform technique produces distinct underfill areas.
The centered scheme shows some defects due to inaccurate control of extreme deposition widths.
The inward distributed scheme produces the least defects.
}
\label{prints}
\end{figure}
}{}

>>>>

{
\subsection{Computational results}\label{sec_computational_results}
} % tew
We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
The data set is described in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices for analysis.
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library,
and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using {$N=2$}, all with a preferred bead width{} of {$w^* = \SI{0.5}{\milli\meter}$ and using the widening meta-scheme to enforce a minimum printed feature size of $w_\text{min}=2r_\text{min}=\SI{0.3}{\milli\meter}$}.
The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.
{We report on the total statistics summed over the whole data set, because averaging would be biased.}

\subsubsection{Accuracy}
We first evaluate the accuracy of different beading schemes in terms of the relative amount of the overfill and underfill. 
We construct the over- and underfill area by comparing the shapes covered by each extrusion move  with each other and with the total shape of the boundary polygons. (For implementation details see Appendix~\ref{accuracy_calculation}.)
This results in polygonal shapes such as visualized in the top half of \cref{visualized_accuracy}:
there are orange shapes where the beads overlap and azure shapes in the voids in between the beads.
%
%
We compare the total area in \si{\milli\meter\squared} of these overfill and underfill shapes to the total area of the boundary for each sample in the data set
and report the average percentages in \cref{over_underfill}.
The inward distributed scheme has a calculated overfill of {\SI{0.30}{\percent}} and an underfill of {\SI{0.24}{\percent}}.
This is lower compared to the uniform scheme, which results in {\SI{1.63}{\percent}} overfill and {\SI{1.62}{\percent}} underfill in the data set.
\iffalse
names ['naive', 'Constant', 'Center', 'Distributed', 'InwardDistributed']
overfill [  1.63223926  22.21073295   0.37059604   0.45119725   0.30226112]
outer_underfill [ 0.04664107  0.03232884  0.04357603  0.03494708  0.03475748]
underfill [ 1.62009421  0.0712721   0.76886316  0.2440984   0.24461937]
\fi

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-naive-widths.png}
\caption{Uniform}\label{TEST_naive_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-accuracy.png}
%\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-SingleBead-widths.png}
%\caption{Single}\label{TEST_SingleBead_accuracy}
%\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Constant-widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Center-widths.png}
\caption{Centered}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-Distributed-widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-accuracy.png}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-TEST-InwardDistributed-widths.png}
\caption{Inward {($N=2$)}}\label{TEST_InwardDistributed_accuracy}
\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4.7cm}
\includegraphics[height=\figheight]{sources-validation-gMAT-example-widths-legend.pdf}
\end{subfigure}
\caption{
Visualization of the overfills and underfills (top) and the widths (bottom) for various beading schemes.
Extrusion beads in gray tones,
overfill in orange,
underfill in azure,
narrow beads in blue
and wide beads in red.
{In order to distinguish clearly from the Distributed scheme the Inward is limited to $N=2$.}
}
\label{visualized_accuracy}
\end{figure*}

\begin{figure*}
\centering
\setlength{\figheight}{0.25\textwidth}
\setlength{\figwidth}{0.32\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-over-underfill.pdf}
%\includegraphics[width=\figwidth]{sources-validation-overunderfill.pdf}
\caption{{Over- and underfill}}
\label{over_underfill}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-print-time.pdf}
%\includegraphics[width=\figwidth]{sources-validation-smoothness.pdf}
\caption{{Print time}}
\label{printtime}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-path-counts.pdf}
%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
\caption{{Path counts}}
\label{pathcounts}
\end{subfigure}

\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-widths.pdf}
%\includegraphics[width=\figwidth]{sources-validation-widthHistogram.pdf}
\caption{{Extrusion widths}}
\label{widthHistogram}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-angles.pdf}
%\includegraphics[width=\figwidth]{sources-validation-smoothnessNoTransition.pdf}
\caption{{Site angles}}
\label{smoothness}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources-validation-computime2.pdf}
%\includegraphics[width=\figwidth]{sources-validation-computime2.pdf}
\caption{Computation time}
\label{computime}
\end{subfigure}

\caption{
Statistical analysis of the toolpaths from applying the uniform width technique and various beading schemes using our framework to a data set of 300 slices.
Note the use of a logarithmic scale {in the bottom graphs }on the Y-axes and {for \subref{computime} on} the X-axes as well.
}
\label{statisticsfig}
\end{figure*}

\subsubsection{Uniformity}
We visualize the bead widths resulting from the different schemes in the bottom of \cref{visualized_accuracy}.
{
We binned the toolpaths into width bins at \SI{0.01}{\milli\meter} increments and determine the total toolpath length pertaining to each bin.
From these statistics we calculate the mean and standard deviation and report them in \cref{widthHistogram}.
}
We found that the mean width of the inward and evenly distributed schemes is close to preferred bead width of \SI{400}{\micro\meter}, while their standard deviation is lower than for the centered and constant bead count scheme. 
These results show that, while causing less overfill and underfill, inwards distributed and evenly distributed schemes deviate less or less often from the preferred bead width compared to the other schemes.

{
\subsubsection{Print time}
The total time it takes to print a part is influenced not only by our back pressure compensation scheme, but also by the geometry of the toolpaths.
In order to separate these effects we report on the total print time when using back pressure compensation and when using a constant (maximum) movement speed in \cref{printtime}.
We estimate print times using a simulation of the Marlin firmware using the default movement settings of the setup described in \cref{print_results_section}.
While the idealized print time is predominantly determined by the total toolpath length, the print time using back pressure compensation is predominantly determined by the occurrence of wide beads, because they have a reduced the flow in \si{\milli\meter\cubed\per\second}.
Because of acceleration constraints imposed by the hardware the maximum movement speed is not reached near sharp corners.
We therefore also report on the angles of the bends in the toolpaths in \cref{smoothness}.
Furthermore, the print time is negatively affected by discontinuities in the extrusion process.
Between extrusions the printer needs to stop extrusion, travel to the next extrusion path and restart the extrusion process, which may introduce defects and incurs extra print time.
For closed polygonal toolpaths we can start anywhere within the path, so we can optimize the starting location so as to minimize the travel time.
We therefore report both on the open and closed path count in \cref{pathcounts}.
}

@@

### 2020-01-25 8_discussion.tex
remove \revise macro everywhere

\subsection{Comparison of beading schemes}
We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average approximately \SI{1}{\percent} of the total target area is covered by underfill and likewise for overfill.
To our knowledge, the uniform beading scheme, as well as the outer beading scheme, is of little use to FDM printers.

The constant bead count scheme effectively deals with underfills, but generates orders of magnitude more overfills compared to the other schemes. 
Also, the scheme comes at the cost of greatly varying bead widths and an average bead width that is not close to the preferred bead width.
Note that most overfill areas occur near regions of alternating bead width. 
For an input outline shape which contains both very small and very large features, the constant bead count scheme produces bead widths which can fall outside of the range of manufacturable bead widths.
Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.

In \cref{TEST_Center_accuracy} we can see that
the centered beading scheme \revise{effectively }{}deals with both overfill and underfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths \revise{are within a factor 2 off from the desired bead width.}{range between $0.5 w^*$ and $1.8w^*$, i.e. the variation is within a factor of $3.6$.}
According to \cref{over_underfill} the overfill and underfill for the centered, the evenly distributed and the inward distributed scheme are all approximately \SI{0.2}{\percent}, which is a considerable improvement over the uniform technique.

However, according to \cref{widthHistogram} the centered scheme exhibits a wider range of bead widths than the distributed schemes:
the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.
\revise{}{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, i.e. the variation is within a factor $2$, which is considerably lower the than factor of $3.6$ in the centered scheme.}
We therefore conclude that the distributed schemes \revise{result in bead widths closer to the preferred widths}{exhibit a lower bead width variation} compared to the centered scheme.
%This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.

It is hard to visually identify the difference between the evenly and the inward distributed scheme in \cref{visualized_accuracy}, because that particular example shape does not have wide features.
However, \cref{distributed_comparison} and  \cref{widthIndexedHistogram} confirm that the outer toolpaths have the preferred bead width more often.
Furthermore, from \cref{smoothness} we find that compared to evenly distributed, the inward distributed scheme produces smoother toolpaths overall.
Thus the inward distributed scheme prevents over- and underfill, generates smooth toolpaths with more homogeneous width and affects smaller more centered parts of the print than the other schemes.

\revise{}
{
\subsection{Limitations}
Because the performance of the various toolpathing techniques depends on the geometry of a model, they have ramifications for the practice of design for additive manufacturing.
Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
For the center scheme and for the current state of the art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.5) w^*$ in order to avoid underfill.
For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.
The design consideration therefore reduces to limiting the diameter of your parts to be within the range $[w_\text{min}, \infty)$,
where $w_\text{min}$ is a configurable parameter when using the widening meta-scheme.

@@

\revise{
\subsection{Discussion on implications}
Note that the current industry standard in FDM printing employs little to no bead width variation.
Properly performing bead width variation calls for adaptations and developments in printers and firmware.
In the beading schemes we set a transition length of $t(n) = w^*$.
That will demand changes in cross-sectional area of the bead up to \SI{200}{\percent} over a small distance that is comparable to the nozzle size, which is challenging for some hardware systems.
Varying the movement speed can be utilized to change the cross-sectional area, but this approach is limited, since the movement speed is constrained by acceleration considerations near bends in the toolpath~\cite{Ertay2018,Kuipers2018}.
Our schemes require a more accurate control of the volumetric flow rate in \si{\milli\meter\cubed\per\second}.
Using a filament feeder directly mounted on the print head (a.k.a. direct drive) can control the flow more dynamicaly then FDM printers where the material is fed through a Bowden tube from a feeder mounted on the frame.
Still direct drive printers require some control system in order to accurately change the volumetric flow rate such as pressure advance algorithms~\cite{tronvoll2019investigating}.
Yet inaccuracies in direct drive systems employing advance algorithms might arise due to the changes in back-pressure required by changing bead size.
We expect that developments in printing hardware and firmware will address these challenges in the future.

Another limiting factor for adopting adaptive bead width is the format of G-code which stores machine instructions.
G-code does not support moves with varying cross-sectional area.
A typical extrusion move \lstinline!G1 X$x$ Y$y$ E$v$! only specifies the total amount of volume $v$ to be extruded in the move, not how that total amount should be distributed along the extrusion move.
A workaround is to approximate a variable width extrusion segment by smaller segments with constant width.
However, this introduces errors nevertheless.
Ideally the G-code language would be expanded in some way to allow for extrusion segments with varying cross-sectional area.
}{}

>>>>

\subsection{Comparison of beading schemes}
We can see from \cref{TEST_naive_accuracy}(top) and~\ref{over_underfill} that the uniform technique causes a lot of overfills and underfills: on average  {\SI{1.6}{\percent}} of the total target area is covered by underfill and likewise for overfill.
To our knowledge, the uniform beading scheme, as well as the outer beading scheme, is of little use to FDM printers.

The constant bead count scheme effectively deals with underfills, but generates orders of magnitude more overfills compared to the other schemes. 
Also, the scheme comes at the cost of greatly varying bead widths and an average bead width that is not close to the preferred bead width.
Note that most overfill areas occur near regions of alternating bead width. 
{While the scheme results in short toolpaths, as indicated by the idealized print time, it also results in a wide range of bead widths, which cause the back pressure compensation print time to be very large.
See \cref{statisticsfig}.}
For an input outline shape which contains both very small and very large features, the constant bead count scheme produces bead widths which can fall outside of the range of manufacturable bead widths.
Moreover the centrality marking is not robust against small perturbations in the outline; adding a small chamfer in a corner causes the unmarked ST to be very small at that location, which results in tiny bead widths.
{See top right of \cref{TEST_Constant_accuracy}.}

In \cref{TEST_Center_accuracy} we can see that
the centered beading scheme effectively deals with overfill and produces desired bead widths in all locations, except for the extrusion paths in the center, where the bead widths {range between $0.5 w^*$ and $1.8w^*$, i.e. the variation is within a factor of $3.6$.}
{However, it does produce some narrow underfill regions.}
{
Compared to the uniform technique the centered technique increases the (open) path count, but considerably reduces over- and underfill and decimates the number of toolpath angles below \SI{45}{\degree}.
See \cref{statisticsfig}.
}

However, according to \cref{widthHistogram} the centered scheme exhibits a wider range of bead widths than the distributed schemes:
the standard deviation of the bead widths in the centered scheme is approximately \SI{39}{\micro\meter}, while that of the distributed schemes is approximately \SI{14}{\micro\meter}.%_
{\footnote{{Although the standard deviation $\sigma$ of the inward distributed scheme is slightly higher, the mean absolute deviation is lower than that of the evenly distributed scheme (i.e. \SI{9}{\micro\meter} versus \SI{11}{\micro\meter}), because its distribution is more peaked.}}}
{Moreover, because the quantization operator rounds to the nearest number of beads, in the worst case where we switch from a single to two beads the widths switch from $0.75w^*$ to $1.5w^*$, i.e. the variation is within a factor $2$, which is considerably lower the than factor of $3.6$ in the centered scheme.}
We therefore conclude that the distributed schemes {exhibit a lower bead width variation and lower (open) path count} compared to the centered scheme.
%This is desirable for the manufacturability of the beads and can therefore have a positive effect on the mechanical properties and surface quality of the 3D prints.

{\Cref{distributed_comparison,TEST_Distributed_accuracy,TEST_InwardDistributed_accuracy} show that in the inward distributed scheme the outer toolpaths have the preferred width more often than in the evenly distributed scheme, which means that the outline accuracy of the inward distributed beading is less affected by inaccuracies in the adaptive width control system.}
%{\Cref{TEST_InwardDistributed_accuracy} shows that in the inward distributed scheme the outer beads are more often equal to the preferred width compared to the evenly distributed scheme in \cref{TEST_Distributed_accuracy}, but that effect is more pronounced for wider geometry such as in \cref{distributed_comparison}.}
%While the difference between the evenly and inward distributed scheme in \cref{visualized_accuracy} results only in the outer bead being the preferred width in some locations, the effect of the inward distributed scheme is more pronounced in larger geometry, as can be seen in \cref{distributed_comparison}.}
 % _
Furthermore, we find that compared to evenly distributed, the inward distributed scheme produces {less corners with angles above \SI{130}{\degree} and less overfill, because the area of influence that bead count transitions have is limited in the inward distributed scheme}.
Thus the inward distributed scheme prevents over- and underfill, generates smooth toolpaths with more homogeneous width and affects smaller more centered parts of the print than the other schemes{, while incurring little to no extra print time}.

{
\subsection{Limitations}
Because the performance of the various toolpathing techniques depends on the geometry of a model, they have ramifications for the practice of design for additive manufacturing.
Because the naive method produces under- or overfill for parts of an outline with a constant diameter $d \neq 2 i w^*$ it is best practice to design a model such that horizontal cross-sections have a feature diameter of an even integer multiple $i$ of the bead width.
For the center scheme and for the current state of the art one should only avoid parts for which $(2i + 1.8) w^* < d < (2i + 0.5) w^*$ in order to avoid underfill.
For the distributed schemes however, there is no diameter at which the framework produces under- or overfill for a part with a constant diameter $d$.
The design consideration therefore reduces to limiting the diameter of your parts to be within the range $[w_\text{min}, \infty)$,
where $w_\text{min}$ is a configurable parameter when using the widening meta-scheme.

@@
